---
title: "Vaccines Project"
author: "Maria Freydlin"
date: "5/17/2021"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T)
```

## Introduction

This presentation demonstrates the data manipulation used in my Vaccine Count shiny app. The data set was downloaded from Kaggle and it contains daily Covid-19 vaccinations for each country. You can view the app here [Vaccines](https://mariafreydlin.shinyapps.io/vaccines/)

## Dataset Preview

Here I load all the libraries and take a preview of the dataset

```{r df, message=F, warning=F}

library(dplyr)
library(ggplot2)
library(readr)
df <- read_csv("country_vaccinations.csv.zip")
df
```
## Filter and Group
Filter and Group the data set by date and summarize by total vaccinations per country. In the shiny app the user will choose which country to filter by
```{r filter, message=F, warning=F}
df_total <- df %>% 
        filter(country=="Belarus") %>%
        group_by(date) %>%
        summarise(total = sum(total_vaccinations, na.rm = T))
df_total
```

## Plot the vaccine timeline for the selected country

```{r plot}
g <- ggplot(df_total, aes(date, total)) + geom_line() +theme_bw()
g

```

